PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added PHQ and GAD difference scores for base, retro and prepan

>>>>

#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
PHQ difference scores
```{r phq difference scores}
# Difference score for prepandemic and retrospective phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_retro =
      as.numeric(
        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$phq.diff_score_prepan_retro)

# Difference score for prepandemic and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_prepan_base =
      as.numeric(
        phq.sum_score_prepan - phq.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

summary(dat.glad$phq.diff_score_prepan_base)

# Difference score for retrospective and baseline phq sum scores
dat.glad <- dat.glad %>%
  mutate(
    phq.diff_score_base_retro =
      as.numeric(
        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$phq.diff_score_base_retro)

GAD difference scores
```{r gad difference scores}
# Difference score for prepandemic and retrospective gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_retro =
      as.numeric(
        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
      )
  )

summary(dat.glad$gad.diff_score_prepan_retro)

# Difference score for prepandemic and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_prepan_base =
      as.numeric(
        gad.sum_score_prepan - gad.sum_score_base  # prepandemic sum score MINUS baseline sum score 
      )
  )

summary(dat.glad$gad.diff_score_prepan_base)

# Difference score for retrospective and baseline gad sum scores
dat.glad <- dat.glad %>%
  mutate(
    gad.diff_score_base_retro =
      as.numeric(
        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
      )
  )

summary(dat.glad$gad.diff_score_base_retro)

#Data level groups
Identify which data (prepan, retro and baseline) each participant has
Has only prepandemic == 0
prepandemic and baseline == 1
prepandemic, baseline, and retrospective == 2
++KT: not sure how best to categorise here so this may need some revision. 
```{r data level groups}
dat.glad <- dat.glad %>%
  mutate(
    data_group_full_numeric =
      case_when(
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    data_group_full = 
      recode_factor(
        data_group_full_numeric,
        "0" = "Only prepandemic data",
        "1" = "Prepandemic and baseline data",
        "2" = "Prepandemic, baseline and retrospective PHQ data",
        "3" = "Prepandemic, baseline and retrospective GAD data",
        "4" = "Prepandemic, baseline and retrospective PCL data",
        "5" = "All prepandemic, baseline and retrospective data"
      )
  )

table(dat.glad$data_group_full)
```
